---
title: "HW5"
author: "Zhuodiao Kuang"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, echo = FALSE, cache = FALSE, message = FALSE}
rm(list = ls())
library(knitr)
library(tidyverse)
library(kableExtra)
library(ggplot2)
## Global options
opts_chunk$set(echo      = TRUE,
	             cache     = TRUE,
               prompt    = FALSE,
               tidy      = FALSE,
               comment   = NA,
               message   = FALSE,
               warning   = FALSE,
               dpi       = 150,
               fig.width = 8, 
               fig.asp   = 5/7,
               fig.align = "center")
# attr.source = '.numberLines'
```

# Problem 1

```{r}
library(faraway)
data<-state.x77
head(data)


```

## a) Provide descriptive statistics for all variables of interest (continuous and categorical) – no test required.

matrix with 50 rows and 8 columns giving the following statistics in the respective columns.

**1.Population(continuous): **
population estimate as of July 1, 1975

Min. 1st Qu.  Median    Mean 3rd Qu.    Max.  are presented as follows:

`r summary(data[,1])`


**2.Income(continuous):**
per capita income (1974)

Min. 1st Qu.  Median    Mean 3rd Qu.    Max.  are presented as follows:

`r summary(data[,2])`

**3.Illiteracy(continuous):**
illiteracy (1970, percent of population)

Min. 1st Qu.  Median    Mean 3rd Qu.    Max.  are presented as follows:

`r summary(data[,3])`


**4.Life Exp(continuous):**
life expectancy in years (1969–71)


Min. 1st Qu.  Median    Mean 3rd Qu.    Max.  are presented as follows:

`r summary(data[,4])`


**5.Murder(continuous):**
murder and non-negligent manslaughter rate per 100,000 population (1976)

Min. 1st Qu.  Median    Mean 3rd Qu.    Max.  are presented as follows:

`r summary(data[,5])`


**6.HS Grad(continuous):**
percent high-school graduates (1970)

Min. 1st Qu.  Median    Mean 3rd Qu.    Max.  are presented as follows:

`r summary(data[,6])`

**7.Frost(continuous):**
mean number of days with minimum temperature below freezing (1931–1960) in capital or large city

Min. 1st Qu.  Median    Mean 3rd Qu.    Max.  are presented as follows:

`r summary(data[,7])`



**8.Area(continuous):**
land area in square miles

Min. 1st Qu.  Median    Mean 3rd Qu.    Max.  are presented as follows:

`r summary(data[,8])`


